---
title: Tuvalu
author: Violeta Roizman
date: '2020-10-29'
slug: []
categories: []
tags: []
showDate: yes
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(extrafont)
library(rgeos)
library(sf)
loadfonts(dev = "win")

world <- rnaturalearth::ne_countries(scale = 10, returnclass = "sp")
box_cut <- rgeos::bbox2SP(n = 90, s = -90, w = -70, e = 160, proj4string = world@proj4string)
world_crop <- rgeos::gDifference(world, box_cut)

# pacific_crop <- world_crop %>% 
#   st_as_sf() %>% # change from sp to sf object/class
#   st_shift_longitude() %>% 
#   st_crop(c(xmin = st_bbox(.)[["xmin"]],
#             xmax = st_bbox(.)[["xmax"]],
#             ymin = -20,
#             ymax = 0))
# 
# tiny_countries <- rnaturalearthdata::tiny_countries50 %>% 
#   st_as_sf() %>%
#   st_shift_longitude() %>% 
#   st_crop(c(xmin = 120, xmax = 250, ymin = -50, ymax = 30)) %>% 
#   # Also adds the coordinates to be used for labeling with geom_text_repel
#   bind_cols(st_coordinates(.) %>% as.data.frame())
# 
# ggplot() +
#   geom_sf(data = pacific_crop) +
#   geom_sf(data = tiny_countries, size = 2, color = "red")
# 
# world <- rnaturalearth::ne_countries(scale = 10) %>%
#   st_as_sf() %>%
#   sf::st_shift_longitude() %>% 
#   sf::st_crop(c(xmin = 165,
#             xmax = 188,
#             ymin = -20,
#             ymax = 0))
# 
# rnaturalearthdata::tiny_countries50
# 
# tuvalu <- filter(pacific_crop, name_en == "Tuvalu") 
# 
lighten <- function(color, factor=1.4){
    col <- col2rgb(color)
    col <- col*factor
    col <- rgb(t(col), maxColorValue=255)
    col
}
# 
# tiny_countries <- rnaturalearthdata::tiny_countries50 %>% 
#   st_as_sf() %>%
#   st_shift_longitude() %>% 
#   st_crop(c(xmin = 120, xmax = 250, ymin = -50, ymax = 30)) %>% 
#   # Also adds the coordinates to be used for labeling with geom_text_repel
#   bind_cols(st_coordinates(.) %>% as.data.frame())
# 
paleta = colorspace::rainbow_hcl(10)
# 
# world_crop %>% 
#   st_as_sf() %>% # change from sp to sf object/class
#   st_shift_longitude() %>%
#   st_bbox()


pacific_crop <- world_crop %>% 
  st_as_sf() %>% # change from sp to sf object/class
  st_shift_longitude() %>% 
  st_crop(c(xmin = 120,
            xmax = 220,
            ymin = -50,
            ymax = 30))

tiny_countries <- rnaturalearthdata::tiny_countries50 %>% 
  st_as_sf() %>%
  st_shift_longitude() %>% 
  st_crop(c(xmin = 160, xmax = 220, ymin = -50, ymax = 30)) %>% 
  # Also adds the coordinates to be used for labeling with geom_text_repel
  bind_cols(st_coordinates(.) %>% as.data.frame())

tiny_countries2 <- rnaturalearthdata::tiny_countries50 %>% 
  st_as_sf() %>%
  filter(name == "Tuvalu") %>%
  st_shift_longitude() %>% 
  st_crop(c(xmin = 160, xmax = 220, ymin = -50, ymax = 30)) %>% 
  # Also adds the coordinates to be used for labeling with geom_text_repel
  bind_cols(st_coordinates(.) %>% as.data.frame())



```


Have you ever heard about the country [Tuvalu](https://en.wikipedia.org/wiki/Tuvalu)? Have you ever heard about [Twitch](twitch.tv)? In this post we tell you what they have in common.

You probably heard about the increasingly popular streaming platform Twitch. It has been recently acquired by [Amazon](http://amazon.com/). You may have noticed that domain of the platform is ".tv". Of course, it's a streaming website, right? Have you ever wonder what does it take to put a ".tv" domain on your website? Well, you have to pay for that. And when you pay for that domain you are implicitly paying to Tuvalu. Indeed, Tuvalu is a lucky micro-state whose country internet domain is ".tv". The country government has been selling the rights to use it since a long time.

```{r, echo=FALSE, out.width="100%", fig.width=9, fig.height=5}
ggplot() +
  geom_sf(data = pacific_crop, fill = "lightgray", color = "lightgray") +
  geom_sf(data = tiny_countries2, size = 2, color = paleta[1]) +
  geom_sf(data = tiny_countries, size = 2, color = "red", alpha = 0) +
  coord_sf(expand = FALSE) +
  theme_minimal() +
  theme(panel.background = element_rect(fill = lighten("#272822", 1.4), color = lighten("#272822", 1.4)),
        #panel.border =  element_rect(fill = "#272822", color = "#272822"),
        text = element_text(color = "#ffffff", family = "Didact Gothic"),
        axis.text = element_text(color = "#ffffff", family = "Didact Gothic"),
        panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(), panel.grid.minor.y = element_blank(), 
        plot.background = element_rect(fill = "#272822", color = "#272822"))

```


In 2019, The Washington Post [published](https://www.washingtonpost.com/video-games/2019/12/23/tuvalu-is-tiny-island-nation-people-its-cashing-thanks-twitch/) that Verisign pays around 5 million dollars per year to Tuvalu for the right to administrate the valuable domain (another link in the story: The Washington Post is owned by Jeff Bezos, [the richest man on Earth](https://mkorostoff.github.io/1-pixel-wealth/), who is the Amazon owner and then Twitch owner). Let's see which fraction of Tuvalu's annual gross national income (GNI) represents this ".tv" income.




Tuvalu is not happy with the contract that signed in 2011 with Verisign, which is valid until 2021. Then, the next year could be a great year for Tuvalu if they manage to establish a good new contract given the Twitch explosion.  
